---
title: "Week 2 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))
```

Your objective is to replicate these figures, created using the Cooperative Congressional Election Study data. These figures are similar to those we completed in the lecture videos.

### Put your name here:
'LAI Chi Long'


## Exercise 1

Hints:

* For the x-axis, use the variable "ideo5".

* Make sure you recode the data for the "ideo5" variable to generate the correct names for the x-axis. You will want to consult the codebook.

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Use guides() to drop the legend.

* Make sure the axis labels and figure title are correct.


```{r exercise1,echo=FALSE}
####PUT YOUR CODE HERE
idea <- recode(cces$ideo5, '1' = 'Very liberal', '2' = 'Liberal', '3' = 'Moderate', '4' = 'Conservative', '5' = 'Very conservative')
table(idea)

ggplot(cces, aes(x=idea, fill=idea)) + geom_bar() + guides() +labs(title = 'Respondent Ideology', x = 'idealogy')


```

## Exercise 2

Hints:

* For the x-axis, use the variable "pew_religimp".

* Make sure you recode the data for the "pew_religimp" variable to generate the correct labels for the x-axis. You will want to consult the codebook.

* Rename the column for Ideology to make sure the first letter is upper-case (to make the legend appear correctly).

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Make sure the axis labels and figure title are correct.

```{r exercise2,echo=FALSE}
####PUT YOUR CODE HERE

religion <- recode(cces$pew_religimp, '1'= 'Very imp.' , '2'= 'Somewhat imp.', '3'= 'Not too imp.', '4'= 'Not imp. at all')
ideology <- idea
ggplot(cces, aes(x=religion, fill=ideology)) + geom_bar() +labs(title = 'Importance of Religion by Ideology', x = 'idealogy')

```

## Exercise 3

Instructions:

* For this visualization, you are creating your own data for practice.

* Create a tibble/data frame with three columns: Semester, Student, and Grade.

* There should be six semesters and three students (Amanda, Betty, and Carol)

* Create grades for the students using the runif() command, with values between 80 and 100. Hint: you'll need 18 grades total.

The figure should look approximately like this (your vaules will be slightly different):


```{r exercise3,echo=FALSE}
####PUT YOUR CODE HERE
set.seed(1234)

df <- 
  tibble(
    Semester = 1:6 %>% rep(times = 3),
    Student = c("Amada", "Betty", "Carol") %>% rep(each = 6),
    Grade = runif(18, 80, 100)
  )
df

ggplot(df,(aes(x=Semester, y=Grade, group=Student))) + geom_line() + facet_wrap(~Student)
```
